# `r fontawesome::fa("user-check")` Evaluation. {#sec-evaluation}

Let's see how your final grade $F$ is calculated.

## `r fontawesome::fa("users")` Co-evaluation.

Consider an hypothetical group of four students that worked together in their first assignment $H_1$ for illustration purposes. The group mark is $H_m = 90$, and now they have to complete their co-evaluation. The group members are: Bebito Fiu-Fiu, Baby Yoda, John Doe and Winnie Pooh. Every member assigns a mark to the rest using a simple Google Form. Then, John Doe's co-evaluation mark $mean(C_1)$ is the simple average of his 3 assigned marks. 

In case $mean(C_1) \ge 70$ and the group mark $H_m \ge 70$, then John Doe's individual $H_1$ mark is computed as: $H_1=(0.70 \times H_m)+(0.30 \times mean(C_1))$.

Otherwise, the individual assignment mark will be the lowest of $mean(C_1)$ and $H_m$: $H_1=\mathrm{min}(mean(C_1), H_m)$. 

Using R:

```{r}
fun <- function(C1, Hm) {
  if (mean(C1) >= 70 && Hm >= 70) { 
  H <- (0.7 * Hm) + (0.3 * mean(C1)) } # H is the individual assignment mark.
  else {H <- min(mean(C1), Hm) } # Free-riders are penalized.
  H }
```

Let's evaluate this function in R to see how it works. Assume this co-evaluation is for the $H_1$ and we are calculating John Doe's mark.

```{r}
# Bebito Fiu-Fiu assigns 70 to John Doe.
# Baby Yoda 60 to John Doe.
# Winnie Pooh 70 to John Doe.
C1 <- c(70, 60, 70)
Hm <- 90 # Group mark.
H1 <- fun(C1, Hm) # Individual mark.
paste("John Doe's coevaluation in the first assignment is:", round(mean(C1), 2))
paste("John Doe's individual mark in the first assignment is:", round((H1), 2))
```

This is because we apply $H_1=\mathrm{min}(mean(C_1), H_m) \rightarrow H_1=\mathrm{min}(66.67, 90)\rightarrow H_1=66.67$. 

If instead of 60, Baby Yoda evaluates John Doe with a 80, then:

```{r}
C1 <- c(70, 80, 70)
Hm <- 90 # Group mark.
H1 <- fun(C1, Hm) # Individual mark.
paste("John Doe's coevaluation in the first assignment is:", round(mean(C1), 2))
paste("John Doe's individual mark in the first assignment is:", H1)
```

This is because we apply $H_1=(0.70 \times 90)+\left(0.30 \times \frac{70+80+70}{3}\right) = 85$. Clearly, your co-evaluation matters because although the group mark is 90, John Doe's individual $H_1$ mark could range from 66.67 to 85 depending on Baby Yoda's co-evaluation.






## `r fontawesome::fa("flag-checkered")` Final grade. 

The final grade $F$ is computed as follows:
$$
\begin{aligned}
 F &= 0.4[0.7\mathrm{max}(E_1, E_2) + 0.3\mathrm{min}(E_1, E_2)] \\
 &+ 0.3[0.7\mathrm{max}(H_1, H_2) + 0.3\mathrm{min}(H_1, H_2)] \\
 & + 0.3E_F.
\end{aligned}
$$


## `r fontawesome::fa("hands-helping")` Help. 

In case you have any concern, any question about the course contents, or if you are having trouble understanding the course material, you have to contact me as soon as possible. This is your own responsibility starting from day 1. We can arrange an online meeting, or we can solve your questions or concerns by email, whatever is best. In case you are having a poor academic performance and you are genuinely interested to improve, my best advice is to contact me during the lecture period, not after the last session of the semester, and we can discuss specific strategies that can potentially help you to get higher marks and reduce the risk of failing the course. The point here is that you have to know that I can help you to improve your academic performance during the semester only if you are truly interested. If you would like to improve your marks at a later stage, or after the final exam, then I am afraid I can do nothing for you, but I can do a lot during the semester. Please email me in case you would like to arrange an appointment, my full contact details are at the beginning of this syllabus. The email is definitely the best way to initially approach me.

In case you get a low mark in one activity or you get difficulties at some specific topic you should take immediate actions in order to quickly revert this. I am not planning to relax the marking criterion so what you have to do is to improve your own quality standards in order to pass given my marking standards and my expectations about your academic performance. You are free to contact me in case you need assistance about specific strategies to improve your academic performance.

I do not recommend you to get disappointed, angry or sad if you get a low mark. There is no need for that because getting one low mark is not determinant to fail the course. Please see the evaluation method to verify how the final grade is computed @sec-evaluation and you will be amazed in a positive way. Also, I do not recommend you to get frustrated if you receive an unexpected low mark or an unexpected negative feedback about your work or your answers. The mechanics here are very simple: *in order to improve, understand and learn, you need to know what you did well, what you did wrong, and try again until you do well without getting desperate or frustrated in the process*. In short, avoid negative feelings as these might lead to further frustration. Nobody wants to hurt you, we all want you to learn in a favorable environment. You have overcome challenges before, so avoid the dark side `r fontawesome::fa("ghost")`. On the contrary, you should rather work harder to meet the course standards. We are not in conflict, in fact we are collaborating. According to my experience, students who sadly fail this course ignore or forget these recommendations.

As a student, you may have different responsibilities. You are probably working, you might have family commitments, other courses, unexpected workload, troubles, and other diverse duties. All these may affect your academic performance at some time. My view here is that you are expected to do well in all aspects of your life and you will have to manage your time effectively and be productive. I hope you can allocate your time in such a way that you can pass this course and do well in the rest of your personal activities. Sometimes the workload is so intense that you have to evaluate whether you need to drop an activity to do well in the rest and keep you healthy, physically and mentally. If you find yourself overwhelmed by your personal troubles, workload and responsibilities, please ask for help, the university has professionals that can help you with this. If you have personal problems I can hear you and if I am unable to guide you properly, we can ask for professional help. Keep this in mind, we all care about your health, and health is far more important than a job, a course, and the university.

This is a video from The University of Arizona Global Campus about How to Manage College Stress.

```{r echo=FALSE}
embed_url("https://youtu.be/_2BFj-k__s0?si=B5pTS3Zs0X1EJIUF")
```

We all know that good grades do not necessarily make you a good person or a good professional. One could have difficulties at school but have such a good professional network, or an impressive ability to do business, or an impressive entrepreneurship spirit. However, grades are still quite useful to assess how well you are at meeting some academic standards and how well you manage to understand the relevant topics in your area of expertise. It is more important to be a good person than a good professional, and the graded activities are specifically designed to partially evaluate your technical abilities as a professional. Then, we all assume that you are a good person, and the course activities will help us to evaluate some of the required skills and competences as professionals. Having said that, I hope you can achieve high grades in this course.

In sum, I expect the best academic performance you can achieve, not the average, and definitely not the minimum. This should not be a surprise since you are studying at one of the most prestigious private universities in the country (we belong to a business school with AACSB and AMBA accreditation). If you succeed at delivering your best performance in this course, and I believe you can, then you might be in a better position to eventually tackle business problems including the most interesting and valuable ones which includes those that do not exist yet. I am sure you have done some extraordinary things in the past, you have overcome very hard challenges, so take this course just as another opportunity to unleash your full potential and show me how committed you are with your academic professional training. 

I strongly believe you can learn anything just as this video from Khan Academy indicates:

```{r echo=FALSE}
embed_url("https://youtu.be/JC82Il2cjqA")
```

Most of my previous recommendations in this subsection are for those who are having difficulties with the course. If you are doing fine, then good for you `r fontawesome::fa("thumbs-up")`, try to enjoy the learning process as much as you can. My commitment is that you will have all the support and resources you need to pass the course during the semester; you only have to take them or ask for them during the lecture period, not after the last course session, and follow all my recommendations in this syllabus.



