```{r setup, include=FALSE}
knitr::opts_chunk$set(
  warning = FALSE,
  message = FALSE,
  fig.pos = "H",
  out.extra = ""
)
```

```{r contact-links, echo=FALSE, results='asis'}
xfun::file_string("8 contact.html")
```

```{r last-modified, echo=FALSE, results='asis'}
render_time <- Sys.time()
month_names <- c(
  "January", "February", "March", "April", "May", "June",
  "July", "August", "September", "October", "November", "December"
)
am_pm <- if (as.integer(format(render_time, "%H")) < 12) "am" else "pm"
formatted_modified <- paste0(
  month_names[as.integer(format(render_time, "%m"))],
  " ",
  as.integer(format(render_time, "%d")),
  format(render_time, ", %Y, %H:%M:%S "),
  am_pm,
  "."
)

cat(
  '<div class="home-last-modified">',
  '<span class="home-last-modified-label">Modified</span>',
  '<span class="date-modified">', formatted_modified, '</span>',
  '</div>\n',
  sep = ""
)
```

::: {.home-panel}
This syllabus is the official course guide. It contains the course goals, rules, grading method, schedule, activities, resources, references, and expectations for the semester.

The contents of this syllabus are mandatory for all students enrolled in the course. Not having read or fully reviewed this document does not release the student from the obligation to follow the rules, expectations, and procedures established here.

A course syllabus is an academic document containing relevant information for students. This document serves as your ultimate guide to successfully completing this course. Please read it regularly and carefully. Within this document, you will find a comprehensive description of the course goals, rules, objectives, recommendations, grading details, a detailed schedule, activities, resources, references, and learning outcomes. The objective of this document is to provide you with complete certainty regarding what to expect from this course, starting from day 1 until the final exam. Based on my experience, reading this syllabus is positively correlated with students' performance.
:::
